### 2014-04-01 paper/introduction.tex
moar related work

Pipes can also be used for sending media on a specified route through an object; for example, neon signs are created by evacuated glass tubes formed into a specific path.  Electricity is run through the near-vacuum, and this makes the path visible.  If our maker wants to build such a sign, she can substitute EL wire for the evacuated glass and electricity: she need only design a path for the wire to be fed through and then create pipes along that path.

>>>>

Pipes can also be used for sending media on a specified route through an object; for example, neon signs are created by evacuated glass tubes formed into a specific path.  Electricity is run through the near-vacuum, creating light.  If our maker wants to build such a sign, she can substitute EL wire for the evacuated glass: she need only design a path for it to be fed through and then create pipes along that path.
